### 2020-03-19 README.Rmd
add man/figures folder, move readme image to it

[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![Build Status](https://travis-ci.org/ropensci/taxize.svg?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

The functions in the package that hit a specific API have a prefix and suffix separated by an underscore. They follow the format of `service_whatitdoes`.  For example, `gnr_resolve` uses the Global Names Resolver API to resolve species names.  General functions in the package that don't hit a specific API don't have two words separated by an underscore, e.g., `classification`.

@@

## SOAP

Note that a few data sources require SOAP web services, which are difficult to support in R across all operating systems. These include: Pan-European Species directories Infrastructure and Mycobank. Data sources that use SOAP web services have been moved to `taxizesoap` at <https://github.com/ropensci/taxizesoap>.

@@

	<td style="text-align:left;">"api.phylotastic.org/tnrs"</td>

@@

<a href="https://vimeo.com/92883063"><img src="tools/screencast.png" width="400"></a>

>>>>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![Build Status](https://travis-ci.org/ropensci/taxize.svg?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

The functions in the package that work with a specific API have a prefix and suffix separated by an underscore. They follow the format of `service_whatitdoes`.  For example, `gnr_resolve` uses the Global Names Resolver API to resolve species names.  General functions in the package that don't hit a specific API don't have two words separated by an underscore, e.g., `classification`.

@@

@@

@@

<a href="https://vimeo.com/92883063"><img src="man/figures/screencast.png" width="400"></a>
